
\section{Some  Background}
My interest in computers began sometime around 1982. I was 12 at the
time. My older brother tinkered with a TI/99 4A and an Odyssey game
console. For several Summers, I worked at the family business, an auto
repair shop. 

By the time I was 14, I had saved enough to buy an Apple
//c. The transaction took place at a Dillard's department store. Dillard's
sold apple computers for a brief period back then. The //c
cost around 1200 USD in 1984. In 2016, that would be ${\sim} 3000 USD$.
I had no idea at the time how this purchase would alter my future.
I enjoyed playing Tunnels of Doom on the TI/99, however loading the 
game from a cassette tape took several minutes. I must admit that at
the time, my motivation for buying the apple was simply a better game
machine. I was convinced I would pursue a career in marine 
biology. I have always been fascinated by the ocean. After a brief 
introduction in high school to biology, I realized I found computers 
much more captivating than biology. I am still fascinated by
all things marine/maritime however. Perhaps at some point in the
future, I'll be able to meld these interests into a configuration that
will pay the bills.

\section{Apple ][c - The Early Days}
	Rough Outline
	\begin{itemize}
	\item 6502 ASM
	\item Apple ][ assembler tools
	\item floppy based account management written in 6502 assembler with PRODOS.
	\item Interest in math (immediate application of basic trig in simple vector animations)
	\item Consider grabbing some source code from this time. The
          old //c still worked a couple of years ago. Perhaps those
          ancient floppys can still be read.
       \item Agriplex (sp?) Computer Store in Lubbock - one of the few Apple
         authorized dealers at the time in the area.
       \item Rom chip update required to support unidisk 3.5 drive.
	\end{itemize}
