% Compile with 'pdflatex -shell-escape memories.tex'
%
%
\documentclass[12pt]{report}
\usepackage{url}
\usepackage{hyperref}
\usepackage{moreverb} 		% contains verbatimtab
\title{Software Development 1993 - Present}
\author{Todd Stout}
\date{May 2013}
\begin{document}
\maketitle

\section{Introduction}
I have been involved in software development for most of my life. I do
not however, possess any great insight or wisdom. I have simply worked
in several industries and experienced first-hand many different
technologies along the way.

This is an experiment which serves several selfish purposes. First, I
would like to document the evolution of my thoughts and
\emph{feelings} regarding the creation of software. Second, my writing
skills need attention, and therefore I must practice. This is not a technical
treatise, however technical details will be mentioned frequently.

\pagebreak

%
% This is probably going to get large over time. Consider breaking it up now while it is small. Look here
% for inspiration
% http://tex.stackexchange.com/questions/29577/splitting-a-large-document-into-several-files
%
\section{Some  Background}
My interest in computers began sometime around 1982. I was 12 at the
time. My older brother tinkered with a TI/99 4A and an Odyssey game console.
	\include{ti994a}	
\section{Apple ][c - The Early Days}
	Rough Outline
	\begin{itemize}
	\item 6502 ASM
	\item Apple ][ assembler tools
	\item floppy based account management written in 6502 assembler with PRODOS.
	\item Interest in math (immediate application of basic trig in simple vector animations)
	\item Consider grabbing some source code from this time. The old //c still worked a couple of years ago. Perhaps those ancient floppys can still be read.
	\end{itemize}
	
\section{College 1988-1993}
	Rough Outline
	\begin{itemize}
	\item Calculus - wow
	\item Diff-Eq - wow squared
	\item Discrete Math - useful, but engineering classes focused almost exclusively on calc. I wish now I had 
	learned more in this area...it's never too late!
	\item Digital Design - wow - Bring on the flip-flops! (love those JK state machines)
	\item Operating Systems - neat
	\item Programming - Everything should be written in C (or so I naively thought at the time)
	\item IBM 370 Assembly - general purpose registers ready to do your bidding!
	\item Senior project - what was it again?
	\item Fortran - mention TAMUG summer school cruise. Old IBM desktops secured to tables due to rolling ship
	\end{itemize}

\section{Electronics Industry Co-op Job 1991-1992}
	Rough Outline
	\begin{itemize}
	\item ASIC manufacturing
	\item Mainframe
	\item Apollo workstations
	\item X-Windows
	\item Bourne shell
        \item ISPF panels/Green Screens
	\item the getopt() aha moment
        \item First exposure to layoffs.
        
	\end{itemize}
	
\section{Military Telecom Industry - First "Real" Job October 1993}
	Rough Outline
	\begin{itemize}
	\item Living on brother's couch in Houston for a couple of
          months before finding employment
\include{hard-to-find-bugs-part-1}
	\item PDP 11 - ICC Console
	\item TI C31 DSP
	\item Motorolla 68K
	\item VX-Works
	\item FPGA - xilinx
	\item ROM Burning
	\item ROM emulators
	\item Sync comm RS-422
	\item Tektronix logic probe
	\item Switch architecture Interesting attributes: DUART
          multidrop mode, storing .o files in DB and linking at
          runtime
          \item In Retrospect, the code was very clean compared
            to commercial endeavours. Reflect on why that seems hard
            to achieve these days in the commercial sector.
	\end{itemize}

\section{Commercial Telecom Industry 1995 - 2006}
	Rough Outline
	\begin{itemize}
	\item The telecom boondoogle
	\item C, C++, more C++, then Java, with a smattering of SQL
	\item OO/UML (Why do good pictures almost never precipitate
          good code?)
        \item OO Databases
	\item All encompassing platform attempt
	\item Phoenix project, networking, networking, then PNet, it's all about async IO stupid
	\item CORBA vs DCOM
	\item IQTalk - smalltalk inspiration
	\item The rise of XML (if it has angle brackets, it's got to be good!)
	\item Any code samples from this period? 
          I'm afraid not...damn I wish I had saved some for posterity.
	\end{itemize}

\section{Finance Industry 2006 - 2012}
Rough Outline
\begin{itemize}
\item My First Experience being employed by a Microsoft-Only Shop.
\item MS Office Inertia - Excel/Access/VBA
\item The amount of money in this industry for creating absolutely
  nothing is staggering...
\item Javascript becomes a first-class citizen.
\item 

\end{itemize}

\section{}
\section{Retail Industry 2012 - Present}

% \section{Databases}
% \begin{itemize}
% \item dbtools - go/vs semicolon semicolons and splitting - many headaches  
% \end{itemize}

Created by \LaTeX\	
\end{document}


